Structured Classification for Inverse Reinforcement Learning

### 2012-04-10 klein2012/Rebuttal.txt

We would like to thank the reviewers for their torough reading and their remarks.
We wish to raise the following points to somewhat clarify aspects of our work the reviewers showed concern about :
- LSTDmu is one of many choices for a subroutine to compute \mu_E(s,a). In its on-olicy form (the one used in our paper) it only needs some transitions from the expert to approximate mu_E(s,a) the same way LSTDQ approximate Q^\pi(s,a) for all s and a given some transitions drawn from a policy \pi.
  It can be replaced by a problem dependant more appropriate solution, such as a heuristic on the value of mu_E(s,a) when a \neq \pi_E(s).
  In (Klein et al. 2011) it was used in its off-policy form because of the requirement of the algorithm of (Abbeel et al. 2004) to compute \mu for an arbitrary policy. In problems where the state space exhibits a spatial coherence (e.g. the pendulum) it provides a very good approximation. Less so in some other spaces (e.g. the highway).

- With the pendulum experiment, we show that our method works (quantitative results given line 657) in conditions where state of the art algorithms fail due to lack of information. Quantitatively, (klein et al. 2011) have shown that the algorithm of (Abbeel and Ng 2004) needs 2000 to 3000 more arbitrary samples (not the expert's) in order to work. We lift this requirement with SCIRL.

- We show that our algorithm stands comparison when put in competition with MWAL. The latter has access to every bit of information about the problem whereas our algorithm only uses the expert's transitions.

- In addition to needing far less information than state of the art methods, by using a LSTD-like methode once and for all at the beginning, our algorithm is also computationnaly more efficient than others that require solving a MDP at each iteration. Indeed, solving a MDP implies (e.g. if one uses LSPI) using LSTD more than once. This empirically shows with a ten-fold gain on computation time on a desktop computer compared to MWAL.

- We insist on retrieving the reward because task transfer (getting an agent with different capabilities than the expert's to fulfill the same task) can not be done with a policy. With a reward function on the states, it is possible to train any agent on the problem, even if the action space is different.

- Our algorithm differs from Ratliff et al.'s work in several ways :
  - our data points are transitions, whereas MMP needs whole MDPs and associated values (transition probabilities, feature expectations, etc.),
  - we are not merely replacing mu with an approximation based on \mu_E. We introduce a new way to look at the score function q,
  - any classifier (and not only Taskar et al.'s) using such a parametrized score function could be plugged in our algorithm. The equations looks the same but our approach is different, and the results show so,
  - the way we express the score function q allows us to minimize the risk function using only the feature expectation of the expert which is easy to compute from very little data. MMP needs a lot more information to achieveits goal.

- Assumptions for the analysis are strong, but so are most of the assumptions of most of papers e.g. (Abbel and Ng 2004) also assume they can compute \mu perfectly. They provide results about error propagation, but although we formally don't, we experimentally show that this is not critical.

### 2012-04-12 klein2012/Rebuttal.txt

We would like to thank the reviewers for their thorough reading and their remarks.
We wish to raise the following points to somewhat clarify aspects of our work the reviewers showed concern about.

- As mentioned in the paper, the feature expectation can be seen as a vector of Q-functions, of which each component can be estimated using LSTD. That's what LSTDmu does; this is just a temporal difference algorithm (and not a contribution of this paper, as rightly mentioned). As each component shares the same dynamic, the computational cost is the one of performing LSTD on one component (in O(p^3)), see (Klein et al. 2011). Also, we have the same guarantees for estimating mu_E from expert trajectories than for estimating a Q-function with LSTD in an on-policy setting (e.g., see Lazaric et al, 2010). In (Klein et al. 2011) it was used in its off-policy form because of the requirement of the algorithm of (Abbeel et al. 2004) to compute \mu for an arbitrary policy. The on-policy setting considered in our contribution only requires data from the expert.

- Our algorithm differs from Ratliff et al.'s work in several ways.
  - All approaches build on the structured large margin framework of Taskar et al., but they solve quite different problems.
  - Our labels are actions, MMP's labels are policies. We only need expert transitions whereas MMP needs the whole model (for a set of MDPs, not just one). 
  - We are not merely replacing mu with an approximation based on \mu_E (this is Klein et al). We introduce a new way to look at the score function q, which allows addressing two major problems of IRL.
  - Any classifier (and not only the structured margin framework of Taskar et al. used here) using such a parameterized score function could be plugged in our algorithm.
  - The way we express the score function q allows us to minimize the risk function using only the feature expectation of the expert, which can be estimated solely from expert transitions. MMP needs a lot more information to achieve its goal.
- With the pendulum experiment, we show that our method works (quantitative results given line 657) in conditions where state of the art algorithms fail due to lack of information. Quantitatively, (klein et al. 2011) have shown that the algorithm of (Abbeel and Ng 2004) needs 2000 to 3000 more arbitrary samples (not the expert's) in order to work (this is due to the off-policy learning aspect). We lift this requirement with SCIRL.

- We recognize that the assumptions of the analysis are strong (as discussed in the paper). However, we show that the algorithm computes a reward for which the expert policy is the unique optimal policy, which is not a straightforward problem (even knowing the dynamic and the expert policy). Given that recovering a reward is the problem we address, we think it is valuable, despite the strong assumptions.

@@

- We show that our algorithm stands comparison when put in competition with MWAL. The latter has access to every bit of information about the problem whereas our algorithm only uses the expert's transitions.

- In addition to needing far less information than state of the art methods, by using a LSTD-like method once and for all at the beginning, our algorithm is also computationally more efficient than others that require solving one or more MDP at each iteration. Indeed, solving a MDP implies (e.g. if one uses LSPI) using LSTD more than once. This empirically shows with a ten-fold gain on computation time on a desktop computer compared to MWAL.

- We insist on retrieving the reward because task transfer (getting an agent with different capabilities than the expert's to fulfill the same task) cannot be done with a policy. With a reward function on the states, it is possible to train any agent on the problem, even if the action space is different.

### 2012-04-12 klein2012/Rebuttal.txt

We would like to thank the reviewers for their thorough reading and their remarks.
We wish to raise the following points to somewhat clarify aspects of our work the reviewers showed concern about.

- As mentioned in the paper, the feature expectation can be seen as a vector of Q-functions, of which each component can be estimated using LSTD. That's what LSTDmu does; this is just a temporal difference algorithm (and not a contribution of this paper, as rightly mentioned). As each component shares the same dynamic, the computational cost is the one of performing LSTD on one component (in O(p^3)), see Klein et al. Also, we have the same guarantees for estimating mu_E from expert trajectories than for estimating a Q-function with LSTD in an on-policy setting (e.g., see Lazaric et al, 2010). In Klein et al. it was used in its off-policy form because of the requirement of the algorithm of (Abbeel et al. 2004) to compute \mu for an arbitrary policy. The on-policy setting considered in our contribution only requires data from the expert.

- As mentionned by reviewer 2, our algorithm is inspired by MMP but differs in several ways. We are not merely combining existing components as assessed by reviewer 3, but introducing a new way to look at the IRL problem.
 - All approaches build on the structured large margin framework of Taskar et al., but they solve quite different problems.
 - Our labels are actions, MMP's labels are policies. We only need expert transitions whereas MMP needs the whole model (for a set of MDPs, not just one). 
 - We are not merely replacing mu with an approximation based on \mu_E (this is Klein et al). We introduce a new way to look at the score function q, which allows addressing two major problems of IRL. 
 - Any classifier (and not only the structured margin framework of Taskar et al. used here) using such a parameterized score function could be plugged in our algorithm. 
 - The way we express the score function q allows us to minimize the risk function using only the feature expectation of the expert evaluated only in states present in the expert's dataset, which can be estimated solely from expert transitions. MMP needs a lot more information to achieve its goal.

- The lack of quantitative results mentionned by reviewer 2 is addressed with the pendulum experiment, we show that our method works (quantitative results given line 657) in conditions where state of the art algorithms fail due to lack of information. Klein et al.'s results (not recalled in our paper due to space constraints) show that the algorithm of Abbeel and Ng needs around 3000 more arbitrary samples (not the expert's) in order to work (this is due to the off-policy learning aspect). We lift this requirement with SCIRL, which is to the best of our knowledge the only algorithm that works in such drastic conditions.

@@

- We recognize that the assumptions of the analysis are strong (as discussed in the paper). However, we show that the algorithm computes a reward for which the expert policy is the unique optimal policy, which is not a straightforward problem (even knowing the dynamic and the expert policy). Given that recovering a reward is the problem we address, we think it is valuable, despite the strong assumptions.

- We show that our algorithm stands comparison when put in competition with MWAL. The latter has access to the system's dynamics whereas our algorithm only uses the expert's transitions. In the light of this, marginally subpar results are indeed a contribution, indeed our algorithm can be used in cases where the lack of information would prohibit the use of MWAL.

- In addition to needing far less information than state of the art methods, by using a LSTD-like method once and for all at the beginning, our algorithm is also computationally more efficient than others that require solving one or more MDP at each iteration. Indeed, solving a MDP implies (e.g. if one uses LSPI) using LSTD more than once. We empirically notice a ten-fold gain on computation time on a desktop computer compared to MWAL.

- To clarify what we meant l.354, we insist on retrieving the reward because task transfer (getting an agent with different capabilities than the expert's to fulfill the same task) cannot be done with a policy. With a reward function on the states, it is possible to train any agent on the problem, even if the action space is different.

### 2012-04-12 klein2012/main.tex
Correction d'une typo mentionnée dans les revues :
Line 286: "1=1" should be "i=1" and N indexes the example rather than the time step here (for MMP).

Quoique je n'ai corrigé que la première partie, je comprends pas bien ce qu'il a voulu dire dans la seconde...
Mise en page d'EWRL

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% ICML 2012 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Use the following line _only_ if you're still using LaTeX 2.09.
%\documentstyle[icml2012,epsf,natbib]{article}
% If you rely on Latex2e packages, like most moden people use this:
\documentclass{article}

% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{url}
\newcommand{\theHalgorithm}{\arabic{algorithm}}
\usepackage{icml2012}
\mathtoolsset{showonlyrefs=true}

\newtheorem{definition}{Définition}
\newtheorem{lemme}{Lemma}
\newtheorem{theorem}{Théorème}
\newtheorem{hypo}{Hypothèse}
\newtheorem{cor}{Corollaire}
\newtheorem{prop}{Proposition}
\newtheorem{exemple}{Exemple}
\newtheorem{remarques}{Remarques}
\newtheorem{remarque}{Remarque}
\newtheorem{assumption}{Assumption}
\newtheorem{problem}{Problème}
\newtheorem{algo}{Algorithme}
\newtheorem{preuve}{Démonstration}
\newcommand{\argmax}{\operatorname*{argmax}} %\operatorname* pour les op. pouvant admettre des limites...
\newcommand{\argmin}{\operatorname*{argmin}}
\newcommand{\minp}{\operatorname*{min_+}}
\newcommand{\dom}{\operatorname*{dom}}
\newcommand{\Ker}{\operatorname*{Ker}}
\newcommand{\trace}{\operatorname*{trace}}
\newcommand{\cov}{\operatorname{cov}}
\newcommand{\epi}{\operatorname{epi}}
\newcommand{\card}{\operatorname*{Card}}
\newcommand{\conv}{\operatorname*{Conv}}
\newcommand{\vect}{\operatorname*{Vect}}
\newcommand{\var}{\operatorname{Var}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\erf}{\operatorname{erf}}
\newcommand{\bound}{\operatorname*{bound}}
\newcommand{\vpi}{\operatorname{VPI}}
\newcommand{\gn}{\operatorname{Gain}}
\newcommand{\p}{\operatorname{Pr}}
\newcommand{\mlp}{\operatorname{MLP}}
\newcommand*\tto[2]{\smash{\mathop{\longrightarrow}\limits_{#1}^{#2}}}
\newcommand*\ntto[2]{\smash{\mathop{\nrightarrow}\limits_{#1}^{#2}}}
\newcommand{\X}{\mathbf{X}}
\newcommand{\Q}{\mathbf{Q}}
\newcommand{\A}{\mathbf{A}}
\newcommand{\Z}{\mathbf{Z}}
\newcommand{\Y}{\mathbf{Y}}
\newcommand{\E}{\mathbf{E}}
\newcommand{\K}{\mathbf{K}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bb}{\mathbf{b}}
\newcommand{\bc}{\mathbf{c}}
\newcommand{\bd}{\mathbf{d}}
\newcommand{\be}{\mathbf{e}}
\newcommand{\af}{\mathbf{f}}
\newcommand{\bg}{\mathbf{g}}
\newcommand{\bh}{\mathbf{h}}
\newcommand{\bi}{\mathbf{i}}
\newcommand{\bj}{\mathbf{j}}
\newcommand{\bk}{\mathbf{k}}
\newcommand{\bl}{\mathbf{l}}
\newcommand{\bm}{\mathbf{m}}
\newcommand{\bn}{\mathbf{n}}
\newcommand{\bo}{\mathbf{o}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\bq}{\mathbf{q}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bs}{\mathbf{s}}
\newcommand{\bt}{\mathbf{t}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\bv}{\mathbf{v}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bz}{\mathbf{z}}
\newcommand{\ma}{\mathbf{A}}
\newcommand{\mb}{\mathbf{B}}
\newcommand{\mc}{\mathbf{C}}
\newcommand{\md}{\mathbf{D}}
\newcommand{\me}{\mathbf{E}}
\newcommand{\mf}{\mathbf{F}}
\newcommand{\mg}{\mathbf{G}}
\newcommand{\mh}{\mathbf{H}}
\newcommand{\mi}{\mathbf{I}}
\newcommand{\mj}{\mathbf{J}}
\newcommand{\mk}{\mathbf{K}}
\newcommand{\ml}{\mathbf{L}}
\newcommand{\mm}{\mathbf{M}}
\newcommand{\mn}{\mathbf{N}}
\newcommand{\mo}{\mathbf{O}}
\newcommand{\Mp}{\mathbf{P}}
\newcommand{\mq}{\mathbf{Q}}
\newcommand{\mr}{\mathbf{R}}
\newcommand{\ms}{\mathbf{S}}
\newcommand{\mt}{\mathbf{T}}
\newcommand{\Mu}{\mathbf{U}}
\newcommand{\mv}{\mathbf{V}}
\newcommand{\mw}{\mathbf{W}}
\newcommand{\mx}{\mathbf{X}}
\newcommand{\my}{\mathbf{Y}}
\newcommand{\mz}{\mathbf{Z}}
\newcommand{\tphi}{\tilde{\Phi}}
\newcommand{\espace}{\text{ }}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Titre court si le titre fait plus de 40 caractères
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\shorttitle{Classification structurée pour l'ARI}
%
%\shortouvrage{CAp 2012}

% Titre, auteur, pas de date

%\title{Classification structurée pour l'apprentissage par renforcement inverse}
%
%\author{\fontsize{12}{12}\selectfont{Edouard Klein\inst{1}$^,$\inst{2}, Bilal Piot \inst{1}$^,$\inst{3}, Matthieu Geist\inst{1}, Olivier Pietquin\inst{1}$^,$\inst{3}}}
%
%\institute{
%Sup\'elec, IMS Research group, France, \texttt{prenom.nom@supelec.fr}
%\and
%Equipe ABC,
%LORIA, France
%\and
%UMI 2958
%GeorgiaTech-CNRS, France
%}
\icmltitlerunning{Structured Classification for Inverse
Reinforcement Learning}

@@

\twocolumn[ \icmltitle{Structured Classification for Inverse
Reinforcement Learning}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2012
% package.
\icmlauthor{Your Name}{email@yourdomain.edu}
\icmladdress{Your Fantastic Institute,
            314159 Pi St., Palo Alto, CA 94306 USA}
\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
\icmladdress{Their Fantastic Institute,
            27182 Exp St., Toronto, ON M6H 2T1 CANADA}

% You may provide any keywords that you
% find helpful for describing your paper; these are used to populate
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{inverse reinforcement learning, structured multi-class
classification}

\vskip 0.3in
]

\begin{abstract}
This paper addresses the Inverse Reinforcement Learning (IRL)
problem which is a particular case of learning from demonstrations.
The IRL framework assumes that an expert, demonstrating a task, is
acting optimally with respect to an unknown reward function to be
discovered. Unlike most of existing IRL algorithms, the proposed
approach doesn't require any of the following: complete trajectories
from the expert, a generative model of the environment, the
knowledge of the transition probabilities, the ability to repeatedly
solve the forward Reinforcement Learning (RL) problem, the expert's
policy anywhere in the state space. Using a classification approach
in which the structure of the underlying Markov Decision Process
(MDP) is implicitly injected, we end-up with an efficient
subgradient descent-based algorithm.
% whose computational and sample
%complexities are low.
In addition, only a small amount of expert
demonstrations (not even in the form of trajectories but simple
transitions) is required.
%A formal analysis of the algorithm as well as empirical
%demonstrations on two classic but challenging problems are provided.
\end{abstract}
%%%%%
\section{Introduction}
%%%%%
%Dans cette contribution, nous nous plaçons dans le contexte de l'apprentissage par démonstration. Dans ce cadre, un agent artificiel apprend à reproduire une tâche grâce à l'observation d'un expert réalisant cette tâche de manière optimale. Pour trouver une solution à ce problème, nous nous proposons d'utiliser le paradigme de l'apprentissage par renforcement inverse. On suppose alors que l'expert agit de manière à être récompensé pour son comportement relativement à une fonction de récompense inconnue. Le but de l'agent est alors d'inférer cette fonction des démonstrations données par l'expert pour ensuite optimiser son comportement relativement à cette fonction lui aussi.\\

@@

Another approach consists in casting imitation learning into a
multi-class classification problem, introducing in some way the
structure of the MDP. For example, in~\cite{melo2010learning}, the
agent policy is learnt as the solution of a classification problem.
They consider a kernel function built on some induced MDP metric,
which may be combersome to compute. Closest to our proposed
contribution is the Maximum Margin Planning (MMP)
algorithm~\cite{ratliff2006maximum}, which is a classification-based
algorithm associating optimal policies to MDPs. More precisely, the
training set is made of $N$ couples $(\mathcal{M}_i,\pi^*_i)$, with
$\mathcal{M}_i$ an MDP (without reward) and $\pi_i^*$ the associated
optimal policy. Let $\mu^\pi_{d_0,\mathcal{M}_i}$ be the feature
expectation for the policy $\pi$, the initial distribution $d_0$ and
the dynamics induced by the related MDP. Let also
$\mathcal{L}_{\mathcal{M}_i,\pi}$ be a positive and user-defined
margin function penalizing non-optimal policies. MMP minimizes the
following cost function:
\begin{equation}
  J(\theta) = \frac{1}{N}\sum_{1=1}^N \max_\pi(\theta^T
  \mu^\pi_{d_0,\mathcal{M}_i} + \mathcal{L}_{\mathcal{M}_i,\pi}) - \theta^T
  \mu^{\pi_i^*}_{d_0,\mathcal{M}_i}.\nonumber
\end{equation}
This implies solving a set of MDPs at each iteration. At the other
extreme, a similar cost function is considered
in~\cite{ratliff2007imitation}, which searches for a score function
$q$ associating expert actions to states. The training set being $N$
couples $(s_i,a_i=\pi^E(s_i))$ and $l(s,a)$ being a positive
user-defined margin function penalizing non-optimal actions, the
cost function is
\begin{equation}
  J(q) = \frac{1}{N}\sum_{i=1}^N \max_a (q(s_i,a) +
  l(s_i,a))-q(s_i,a_i).\nonumber
\end{equation}
The drawback of this approach is that it does not take into account
the structure of the underlying MDP, which may easily be shown
experimentally to be a problem (\textit{e.g.},
see~\cite{melo2010learning}).

@@

\bibliography{Biblio}
\bibliographystyle{icml2012}
\end{document}

>>>>

%\documentclass[gray]{jmlr} % test grayscale version
\documentclass[tablecaption=bottom]{jmlr}

% The following packages will be automatically loaded:
% amsmath, amssymb, natbib, graphicx, url, algorithm2e

%\usepackage{rotating}% for sideways figures and tables
%\usepackage{longtable}% for long tables

% The booktabs package is used by this sample document
% (it provides \toprule, \midrule and \bottomrule).
% Remove the next line if you don't require it.
\usepackage{booktabs}
% The siunitx package is used by this sample document
% to align numbers in a column by their decimal point.
% Remove the next line if you don't require it.
\usepackage[load-configurations=version-1]{siunitx} % newer version
%\usepackage{siunitx}
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
%\usepackage{subfigure}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{algorithmic}
%\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{url}
%\newcommand{\theHalgorithm}{\arabic{algorithm}}
\mathtoolsset{showonlyrefs=true}

%\newtheorem{definition}{Définition}
\newtheorem{lemme}{Lemma}
%\newtheorem{theorem}{Théorème}
%% \newtheorem{hypo}{Hypothèse}
%% \newtheorem{cor}{Corollaire}
\newtheorem{prop}{Proposition}
%% \newtheorem{exemple}{Exemple}
%% \newtheorem{remarques}{Remarques}
%% \newtheorem{remarque}{Remarque}
\newtheorem{assumption}{Assumption}
%% \newtheorem{problem}{Problème}
%% \newtheorem{algo}{Algorithme}
%% \newtheorem{preuve}{Démonstration}
\newcommand{\argmax}{\operatorname*{argmax}} %\operatorname* pour les op. pouvant admettre des limites...
\newcommand{\argmin}{\operatorname*{argmin}}
\newcommand{\minp}{\operatorname*{min_+}}
\newcommand{\dom}{\operatorname*{dom}}
\newcommand{\Ker}{\operatorname*{Ker}}
\newcommand{\trace}{\operatorname*{trace}}
\newcommand{\cov}{\operatorname{cov}}
\newcommand{\epi}{\operatorname{epi}}
\newcommand{\card}{\operatorname*{Card}}
\newcommand{\conv}{\operatorname*{Conv}}
\newcommand{\vect}{\operatorname*{Vect}}
\newcommand{\var}{\operatorname{Var}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\erf}{\operatorname{erf}}
\newcommand{\bound}{\operatorname*{bound}}
\newcommand{\vpi}{\operatorname{VPI}}
\newcommand{\gn}{\operatorname{Gain}}
\newcommand{\p}{\operatorname{Pr}}
\newcommand{\mlp}{\operatorname{MLP}}
\newcommand*\tto[2]{\smash{\mathop{\longrightarrow}\limits_{#1}^{#2}}}
\newcommand*\ntto[2]{\smash{\mathop{\nrightarrow}\limits_{#1}^{#2}}}
\newcommand{\X}{\mathbf{X}}
\newcommand{\Q}{\mathbf{Q}}
\newcommand{\A}{\mathbf{A}}
\newcommand{\Z}{\mathbf{Z}}
\newcommand{\Y}{\mathbf{Y}}
\newcommand{\E}{\mathbf{E}}
\newcommand{\K}{\mathbf{K}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bb}{\mathbf{b}}
\newcommand{\bc}{\mathbf{c}}
\newcommand{\bd}{\mathbf{d}}
\newcommand{\be}{\mathbf{e}}
\newcommand{\af}{\mathbf{f}}
\newcommand{\bg}{\mathbf{g}}
\newcommand{\bh}{\mathbf{h}}
\newcommand{\bi}{\mathbf{i}}
\newcommand{\bj}{\mathbf{j}}
\newcommand{\bk}{\mathbf{k}}
\newcommand{\bl}{\mathbf{l}}
\newcommand{\bm}{\mathbf{m}}
\newcommand{\bn}{\mathbf{n}}
\newcommand{\bo}{\mathbf{o}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\bq}{\mathbf{q}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bs}{\mathbf{s}}
\newcommand{\bt}{\mathbf{t}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\bv}{\mathbf{v}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bz}{\mathbf{z}}
\newcommand{\ma}{\mathbf{A}}
\newcommand{\mb}{\mathbf{B}}
\newcommand{\mc}{\mathbf{C}}
\newcommand{\md}{\mathbf{D}}
\newcommand{\me}{\mathbf{E}}
\newcommand{\mf}{\mathbf{F}}
\newcommand{\mg}{\mathbf{G}}
\newcommand{\mh}{\mathbf{H}}
\newcommand{\mi}{\mathbf{I}}
\newcommand{\mj}{\mathbf{J}}
\newcommand{\mk}{\mathbf{K}}
\newcommand{\ml}{\mathbf{L}}
\newcommand{\mm}{\mathbf{M}}
\newcommand{\mn}{\mathbf{N}}
\newcommand{\mo}{\mathbf{O}}
\newcommand{\Mp}{\mathbf{P}}
\newcommand{\mq}{\mathbf{Q}}
\newcommand{\mr}{\mathbf{R}}
\newcommand{\ms}{\mathbf{S}}
\newcommand{\mt}{\mathbf{T}}
\newcommand{\Mu}{\mathbf{U}}
\newcommand{\mv}{\mathbf{V}}
\newcommand{\mw}{\mathbf{W}}
\newcommand{\mx}{\mathbf{X}}
\newcommand{\my}{\mathbf{Y}}
\newcommand{\mz}{\mathbf{Z}}
\newcommand{\tphi}{\tilde{\Phi}}
\newcommand{\espace}{\text{ }}

@@

\jmlrvolume{vol}
\jmlryear{2012}
\jmlrsubmitted{\today}
\jmlrpublished{}

\title[SCIRL]{Structured Classification for Inverse Reinforcement Learning}

 % Use \Name{Author Name} to specify the name.
 % If the surname contains spaces, enclose the surname
 % in braces, e.g. \Name{John {Smith Jones}} similarly
 % if the name has a "von" part, e.g \Name{Jane {de Winter}}.
 % If the first letter in the forenames is a diacritic
 % enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}

 % \thanks must come after \Name{...} not inside the argument for
 % example \Name{John Smith}\thanks{A note} NOT \Name{John
 % Smith\thanks{A note}}

 % Two authors with the same address
  \author{\Name{Paper under review at ICML}\thanks{No author name provided so as not to breach ICML's double blind process}}

 % Three or more authors with the same address:
 % \author{\Name{Author Name1} \Email{an1@sample.com}\\
 %  \Name{Author Name2} \Email{an2@sample.com}\\
 %  \Name{Author Name3} \Email{an3@sample.com}\\
 %  \Name{Author Name4} \Email{an4@sample.com}\\
 %  \Name{Author Name5} \Email{an5@sample.com}\\
 %  \Name{Author Name6} \Email{an6@sample.com}\\
 %  \Name{Author Name7} \Email{an7@sample.com}\\
 %  \Name{Author Name8} \Email{an8@sample.com}\\
 %  \Name{Author Name9} \Email{an9@sample.com}\\
 %  \Name{Author Name10} \Email{an10@sample.com}\\
 %  \Name{Author Name11} \Email{an11@sample.com}\\
 %  \Name{Author Name12} \Email{an12@sample.com}\\
 %  \Name{Author Name13} \Email{an13@sample.com}\\
 %  \Name{Author Name14} \Email{an14@sample.com}\\
 %  \addr Address}

 % Authors with different addresses:
 % \author{\Name{Author Name1} \Email{abc@sample.com}\\
 % \addr Address 1
 % \AND
 % \Name{Author Name2} \Email{xyz@sample.com}\\
 % \addr Address 2
 %}

%\editor{Editor's name}

@@

\maketitle

\begin{abstract}
This paper addresses the Inverse Reinforcement Learning (IRL)
problem which is a particular case of learning from demonstrations.
The IRL framework assumes that an expert, demonstrating a task, is
acting optimally with respect to an unknown reward function to be
discovered. Unlike most of existing IRL algorithms, the proposed
approach doesn't require any of the following: complete trajectories
from the expert, a generative model of the environment, the
knowledge of the transition probabilities, the ability to repeatedly
solve the forward Reinforcement Learning (RL) problem, the expert's
policy anywhere in the state space. Using a classification approach
in which the structure of the underlying Markov Decision Process
(MDP) is implicitly injected, we end-up with an efficient
subgradient descent-based algorithm.
% whose computational and sample
%complexities are low.
In addition, only a small amount of expert
demonstrations (not even in the form of trajectories but simple
transitions) is required.
%A formal analysis of the algorithm as well as empirical
%demonstrations on two classic but challenging problems are provided.
\end{abstract}
\begin{keywords}
inverse reinforcement learning, structured multi-class
classification
\end{keywords}

%%%%%
\section{Introduction}
%%%%%
%Dans cette contribution, nous nous plaçons dans le contexte de l'apprentissage par démonstration. Dans ce cadre, un agent artificiel apprend à reproduire une tâche grâce à l'observation d'un expert réalisant cette tâche de manière optimale. Pour trouver une solution à ce problème, nous nous proposons d'utiliser le paradigme de l'apprentissage par renforcement inverse. On suppose alors que l'expert agit de manière à être récompensé pour son comportement relativement à une fonction de récompense inconnue. Le but de l'agent est alors d'inférer cette fonction des démonstrations données par l'expert pour ensuite optimiser son comportement relativement à cette fonction lui aussi.\\

@@

Another approach consists in casting imitation learning into a
multi-class classification problem, introducing in some way the
structure of the MDP. For example, in~\cite{melo2010learning}, the
agent policy is learnt as the solution of a classification problem.
They consider a kernel function built on some induced MDP metric,
which may be combersome to compute. Closest to our proposed
contribution is the Maximum Margin Planning (MMP)
algorithm~\cite{ratliff2006maximum}, which is a classification-based
algorithm associating optimal policies to MDPs. More precisely, the
training set is made of $N$ couples $(\mathcal{M}_i,\pi^*_i)$, with
$\mathcal{M}_i$ an MDP (without reward) and $\pi_i^*$ the associated
optimal policy. Let $\mu^\pi_{d_0,\mathcal{M}_i}$ be the feature
expectation for the policy $\pi$, the initial distribution $d_0$ and
the dynamics induced by the related MDP. Let also
$\mathcal{L}_{\mathcal{M}_i,\pi}$ be a positive and user-defined
margin function penalizing non-optimal policies. MMP minimizes the
following cost function:
\begin{equation}
  J(\theta) = \frac{1}{N}\sum_{i=1}^N \max_\pi(\theta^T
  \mu^\pi_{d_0,\mathcal{M}_i} + \mathcal{L}_{\mathcal{M}_i,\pi}) - \theta^T
  \mu^{\pi_i^*}_{d_0,\mathcal{M}_i}.\nonumber
\end{equation}
This implies solving a set of MDPs at each iteration. At the other
extreme, a similar cost function is considered
in~\cite{ratliff2007imitation}, which searches for a score function
$q$ associating expert actions to states. The training set being $N$
couples $(s_i,a_i=\pi^E(s_i))$ and $l(s,a)$ being a positive
user-defined margin function penalizing non-optimal actions, the
cost function is
\begin{equation}
  J(q) = \frac{1}{N}\sum_{i=1}^N \max_a (q(s_i,a) +
  l(s_i,a))-q(s_i,a_i).\nonumber
\end{equation}
The drawback of this approach is that it does not take into account
the structure of the underlying MDP, which may easily be shown
experimentally to be a problem (\textit{e.g.},
see~\cite{melo2010learning}).

@@

\bibliography{Biblio}
%\bibliographystyle{icml2012}
\end{document}
